### 2021-12-14 input/proposal.tex
xas

By reusing \NAME's default behavior, Algorithm~\ref{algo:edges}
enables dynamic consistent partitioning in dynamic networks where
\processes can join, leave, or crash at any time.  Adding a \process
is equivalent to add as many edges as necessary. Since adding an edge
may improve shortest paths, the protocol triggers a competition using
echos of Definition~\ref{def:fbplus}.  Removing a \process is
equivalent to removing all its edges. Removing an edge between two
\processes may invalidate the shortest path of one of involved
\processes plus downstream \processes, or impair the propagation of
staleness notifications. Therefore, the protocol reuses its detection
mechanism of Lemma~\ref{lem:detector} as a solution.
Algorithm~\ref{algo:edges} even extends \NAME to dynamic networks
subject to physical partitioning.

% \TODO{Multiple receipt and multiple delivery}
In terms of number of messages, deleting the $a^{th}$ partition
generates twice as many messages as creating the $a^{th}$ partition:
$\delta$ messages travel through the partition, then $\alpha$ messages
compete to fill the gap \TODO{which is?}. \TODO{What about false
  positives?} Overall, the communication complexity shows that \NAME
scales well to the number of partitions.
%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.

@@

\TODO{In Edge infrastructures comprising tens of thousands of autonomous
systems~\cite{nur2018crossas}, only a small subset of autonomous
systems needs logical partitioning. At any time, an autonomous system
start logical partitioning when a \process from this network becomes a
source.  Then every \process from this network belongs to the
partition of its closest source not only from their own network but
that of adjacent networks that started logical partitioning as well.
At any time, an autonomous system stops logical partitioning when the
last source from this network revokes its status of
source. Eventually, all nodes from this network do not belong to any
partition and the generated traffic stops.}

\TODO{Further scale, follow up of motivations.}

\begin{definition}[Edge infrastructure]
  An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
  interconnected with additional links $\mathcal{E} \in V_1 \times
  V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
  \ldots G_n\}, \mathcal{E} \rangle$. A \emph{gateway} $g$ is a
  \process with at least one link towards another network: $\langle g,
  \_ \rangle \in \mathcal{E}$.
\end{definition}

>>>>

By reusing \NAME's default behavior, Algorithm~\ref{algo:edges}
enables dynamic consistent partitioning in dynamic networks subject to
physical partitioning where \processes can join, leave, or crash at
any time. Adding a \process is equivalent to add as many edges as
necessary. Since adding an edge may improve shortest paths, the
protocol triggers a competition using echos of
Definition~\ref{def:fbplus}.  Removing a \process is equivalent to
removing all its edges. Removing an edge between two \processes may
invalidate the shortest path of one of involved \processes plus
downstream \processes, or impair the propagation of staleness
notifications. Therefore, the protocol reuses its detectors of
Lemma~\ref{lem:detector} to remove irrelevant messages from the
system.

\TODO{Multiple receipt and multiple delivery} In terms of number of
messages, deleting the $a^{th}$ partition generates twice as many
messages as creating the $a^{th}$ partition: $\delta$ messages travel
through the partition, then $\alpha$ messages compete to fill the gap
\TODO{which is?}. \TODO{What about false positives?} Overall, the
communication complexity shows that \NAME scales well to the number of
partitions.
%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.

@@

To further reduce the traffic generated by our DCP protocol, we
leverage that an Edge infrastructure is a network of autonomous
systems, only a small subset of which needs logical partitioning.

\begin{definition}[Edge infrastructure]
  An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
  interconnected with additional links $\mathcal{E} \in V_1 \times
  V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
  \ldots G_n\}, \mathcal{E} \rangle$. A \underline{g}ateway $g$ is a
  \process with at least one link towards another network: $\langle g,
  \_ \rangle \in \mathcal{E}$.
\end{definition}

At any time, an autonomous system start logical partitioning when a
\process from this network becomes a source.  Then every \process from
this network belongs to the partition of its closest source not only
from their own network but that of adjacent networks that started
logical partitioning as well.  At any time, an autonomous system stops
logical partitioning when the last source from this network revokes
its status of source. Eventually, all nodes from this network do not
belong to any partition and the generated traffic stops.
